Blocking-resistant communication\\through domain fronting

### 2014-07-25 docs/meek.tex
More model revisions.

The model includes four actors:
the censor,
the censored client,
the intermediate web service's frontend server (CDN edge server),
and the destination proxy (Tor bridge).
Circumvention is achieved when the client evades the censor to reach
the destination proxy,
because the proxy provides access to anywhere.
The client and destination proxy cooperate with each other.
The intermediate web service does not cooperate with either,
except to the extent that it doesn't collude with the censor.
% The censor's goal is to prevent circumvention.

The censor controls a network and the into and within it.
The censor is able to inspect traffic flowing across all links under its control
and may block or allow any packet.
The censor may inject and replay traffic, and
operate its own clients and servers.
The client lies within the censor's network,
while the intermediate web service and destination proxy lie outside the network.
The censor blocks direct communication between the client and the destination proxy,
but allows HTTPS between the client and at least one front domain or IP address
on the intermediate web service.

@@

See Section~\ref{sec:security} for what happens when some
of these assumptions are violated;
specifically what happens
when the intermediate web service's frontend server is inside the censor's network
and when the censor controls a certificate authority.

>>>>

The model includes four actors:
the censor,
the censored client,
the intermediate web service (CDN),
and the destination Tor bridge.
Circumvention is achieved when the client evades the censor to reach
the bridge,
because the bridge proxies to anywhere.
The client and bridge cooperate with each other.
The intermediate web service does not cooperate with either,
except to the extent that it doesn't collude with the censor.
% The censor's goal is to prevent circumvention.

The censor controls a network and the into and within it.
The censor is able to inspect traffic flowing across all links under its control
and may block or allow any packet.
The censor may inject and replay traffic, and
operate its own clients and servers.
The client lies within the censor's network,
while the intermediate web service and bridge lie outside the network.
The censor blocks direct communication between the client and the bridge,
but allows HTTPS between the client and at least one front domain or IP address
on the intermediate web service.
% In examples, we will use the \textbf{allowed.example} as the front domain
% and \textbf{forbidden.example} as the domain name of the Tor bridge.

@@

Section~\ref{sec:security} shows what happens when some
of these assumptions are violated;
specifically what happens
when the intermediate web service's frontend server is inside the censor's network
and when the censor controls a certificate authority.
That section also describes the use of meek apart from Tor.
